---
title: "Vignette for mgraph.R - a mini graph module"
author: Detlef Groth
date: 2022-05-07
---

<center>Module documentation: [mgraph.R](mgraph.html)</center>

## Introduction

This is the vignette for the file _mgraph.R_ which provides basic functionalities to work with graphs in R. 

There are several good R packages like [igraph] or [network] which should be
used for serious R programming. The purpose of the graph module _mgraph.R_ is
nore educational. The file is used in my teachings at the University of
Potsdam in the courses _Machine Learning in Bioinformatics_, _Statistical
Bioinformatics_ and _Practical Bioinformatics_. The students should have the
possibility to easily study and learn from R code and the implementations for
several algorithms. The embedded documentation should as well convince the
students from documenting their own code properly.

## Loading the module

The module _mgraph.R_ contains functions to create certain graph types and as
well methods to create graphs from data. Before you start you have usually to
source the file from within your R session. All methods and variables are
stored with the R environment _mgraph_. You can inspect what is available within the _mgraph_
object using the ls function.

```{r}
source('mgraph.R')
ls() # all variables - might vary between machines
ls(mgraph)  # module methods and variables
```

Uppercase objects are usually variables which should not be modified or
private functions which should not be called from the user.  Here we just output the current version of the module.

```{r}
print(mgraph$VERSION)
```

## Graph generation

There is a main method for creating graphs from scratch, it is the method [mgraph$new](mgraph.html#new).

```{r label=new,fig=TRUE,fig.width=9,fig.height=9}
set.seed(123)
par(mfrow=c(2,2),mai=rep(0.1,4))
A=mgraph$new(type="random",nodes=8,edges=12)
B=mgraph$new(type="barabasi",nodes=8,m=1)
C=mgraph$new(type="cluster",nodes=8,edges=8,k=2)
D=mgraph$new(type="regular",nodes=8,k=3)  
plot(A);plot(B);plot(C);plot(D,layout="circle")  
```


## TODO's

foo bar


## EOF



